Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-03-26 ms.tex
typo

\item 201546283.01--- For this system, the ``maximum depth// is nearly 
identical to the observed transit depth, which would require a perfectly
V-shaped eclipse to explain.  As this is not the case (see Figure 2), 
this signal cannot
be caused by contamination from this star.

>>>>

\item 201546283.01--- For this system, the ``maximum depth'' is nearly 
identical to the observed transit depth, which would require a perfectly
V-shaped eclipse to explain.  As this is not the case (see Figure 2), 
this signal cannot
be caused by contamination from this star.
